Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-02 paper.tex

            \tristan{Mentioning fault tolerance would be wise too.}

@@

            Unless a user is building a workflow exclusively based on custom
            functions or using a monolithic workflow engine such as SPM, they
            will need to install the tools necessary for their workflow on
            their computer or cluster \tristan{replace computer or cluster by infrastructure?}. Depending on the workflow engine 
            selected, this may be managed by the engine, or the user may be 
            left to install the dependencies themselves. Workflow engines that
            delegate tool installation to the user include: Nipype, PSOM,

>>>>

            \tristan{Mentioning fault tolerance would be wise too.}
            \tristan{How about: burst buffers, pilot jobs, deployments of Spark on HPC?}

@@

            Unless building a workflow exclusively based on custom
            functions or using a monolithic workflow engine such as SPM, users
            will need to install the tools necessary for their workflow on
            their infrastructure. Depending on the workflow engine 
            selected, this may be managed by the engine or performed manually 
            by the user. Most install the dependencies themselves. Workflow engines that
            delegate tool installation to the user include: Nipype, PSOM,
